{\bf \huge Wikiplia}:\\ The Free Programming Language\\ That Anyone Can Edit

### 2007-03-15 wikiplia/paper/wikiplia.tex
a little bit more

\caption{Evaluation of XML, part 1. The judgment $\G \vdash \eval X \m X'$
indicates an assessment of the document $X$ with value $X'$. The
judgment $\rate$ is an auxiliary assessment of a list of documents. It is defined in Figure~\ref{fig:xmlrate}.
$\vec{X}$ is shorthand for a possibly empty sequence of XML documents.
$\G$ is itself an XML document of the form
% XXX is this right wrt <symbol>?
$\tag{list}{\tag{symbol}{s_1}\ X_1\ \ldots\ \tag{symbol}{s_n}\ X_n}$.
We take the judgment $\G(s) = X$ to produce the leftmost $X_i$ in $\G$
such that $s_i$ is $s$. $\G, s = X$ is $\tag{list}{\tag{symbol}{s}\ X
\vec{X}}$ if $\G$ is $\tag{list}{\vec{X}}$. 
%
} \label{fig:xmleval}
\end{figure*}

@@

Wikiplia is built upon a core calculus of structured data with
primitive revision control. Because we wish to support the freedom to
tinker, the structured data take the form of XML (the {\em extensible}
markup language; Figure~\ref{fig:xml}). Similar to the W3C's XML
Validation,\z\wcite{XML schema} we allow the quality of an XML
document to be assessed via a process called {\em evaluation}, whose
output (if any) is itself an XML document. The rules for XML
evaluation are simple and are given in
Figures~\ref{fig:xmleval}~and~\ref{fig:xmlrate}.

>>>>

\caption{Evaluation of XML, part 1. The judgment $\G \vdash \eval X \m X'$
indicates an assessment of the document $X$ with value $X'$. The
judgment $\rate$ is an auxiliary assessment of a list of documents. It is defined in Figure~\ref{fig:xmlrate}.
$\vec{X}$ is shorthand for a possibly empty sequence of XML documents.
$\G$ is itself an XML document of the form
% XXX is this right wrt <symbol>?
$\tag{list}{\tag{symbol}{s_1}\ X_1\ \ldots\ \tag{symbol}{s_n}\ X_n}$.
We take the judgment $\G(s) = X$ to produce the leftmost $X_i$ in $\G$
such that $s_i$ is $s$. $\G, s = X$ is $\tag{list}{\tag{symbol}{s}\ X
\vec{X}}$ if $\G$ is $\tag{list}{\vec{X}}$. The judgment $s\prim$ holds when
$s$ is one of 
{\sf insert},
{\sf head},
{\sf read},
{\sf abort},
{\sf lambda},
{\sf list},
{\sf cons},
{\sf quote},
{\sf string},
{\sf xcase},
{\sf size},
{\sf sub},
{\sf substr},
{\sf handle},
{\sf parse},
{\sf eval},
{\sf eq},
{\sf +},
{\sf -},
{\sf int},
{\sf history},
{\sf let}, or
{\sf if}.
%
} \label{fig:xmleval}
\end{figure*}

@@

Wikiplia is built upon a core calculus of structured data with
primitive revision control. Because we wish to support the freedom to
tinker, the structured data take the form of XML (the {\em extensible}
markup language; Figure~\ref{fig:xml}). Similar to the W3C's XML
Validation,\z\wcite{XML schema} we allow the quality of an XML
document to be assessed via a process called {\em evaluation}, whose
output (if any) is itself an XML document. Selected rules for XML
evaluation are simple and are given in
Figures~\ref{fig:xmleval}~and~\ref{fig:xmlrate}.\z\footnote{XML
documents can be self-correcting through the use of the {\sf handle}
primitive, which detects an invalid document and proceeds along an
alternative path. We omit the rules for this feature, which requires
propagating invalid document status throughout evaluation and thus
complicates the rules substantially.}

Revision control is accessed through the class of {\tt cvs} judgments.
We assume a single global repository, which maps {\em keys} (strings)
to lists of {\em revisions}. A revision is a monotonically increasing
and unique {\em revision number} (integer) paired with an XML
document. The judgment ${\tt cvs commit}\ s\ X = i$ creates a new
revision with revision number $i$ and data $X$ and inserts it in under
the key $s$.
